Exploring Feature Engineering

### 2019-03-22 Scripts/evaluating_correlations.Rmd
editted correlation script

>>>>

## Stratifying by annotation group (using pca data--flanked TAD boundaries)

##### Counts

```{r}
pcadat_gm12878_10kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_count.rds")

colnames(pcadat_gm12878_10kb_count) <- gsub("_count","",colnames(pcadat_gm12878_10kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_10kb_count_chromstates <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_10kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_chromstates))

cormat <- cor(pcadat_gm12878_10kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_10kb_count_histones <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% histonevars)]

colnames(pcadat_gm12878_10kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_histones))

cormat <- cor(pcadat_gm12878_10kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_10kb_count_tfbs <- pcadat_gm12878_10kb_count[,which(colnames(pcadat_gm12878_10kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_10kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_count_tfbs))

cormat <- cor(pcadat_gm12878_10kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### Percents

```{r}
pcadat_gm12878_10kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_perc.rds")

colnames(pcadat_gm12878_10kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_10kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_10kb_perc_chromstates <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_10kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_chromstates))

cormat <- cor(pcadat_gm12878_10kb_perc_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_10kb_perc_histones <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% histonevars)]

colnames(pcadat_gm12878_10kb_perc_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_histones))

cormat <- cor(pcadat_gm12878_10kb_perc_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_10kb_perc_tfbs <- pcadat_gm12878_10kb_perc[,which(colnames(pcadat_gm12878_10kb_perc) %in% tfbsvars)]

colnames(pcadat_gm12878_10kb_perc_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_perc_tfbs))

cormat <- cor(pcadat_gm12878_10kb_perc_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

####Distances

```{r}
pcadat_gm12878_10kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/Ensemble/PCA/pcadat_gm12878_10kb_dist.rds")

colnames(pcadat_gm12878_10kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_10kb_dist))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_10kb_dist_chromstates <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% chromstatevars)]

colnames(pcadat_gm12878_10kb_dist_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_chromstates))

cormat <- cor(pcadat_gm12878_10kb_dist_chromstates, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_10kb_dist_histones <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% histonevars)]

colnames(pcadat_gm12878_10kb_dist_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_histones))

cormat <- cor(pcadat_gm12878_10kb_dist_histones, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_10kb_dist_tfbs <- pcadat_gm12878_10kb_dist[,which(colnames(pcadat_gm12878_10kb_dist) %in% tfbsvars)]

colnames(pcadat_gm12878_10kb_dist_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_10kb_dist_tfbs))

cormat <- cor(pcadat_gm12878_10kb_dist_tfbs, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### Counts

```{r}
pcadat_gm12878_25kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_count.rds")

colnames(pcadat_gm12878_25kb_count) <- gsub("_count","",colnames(pcadat_gm12878_25kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_25kb_count_chromstates <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_25kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_chromstates))

cormat <- cor(pcadat_gm12878_25kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_25kb_count_histones <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% histonevars)]

colnames(pcadat_gm12878_25kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_histones))

cormat <- cor(pcadat_gm12878_25kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_25kb_count_tfbs <- pcadat_gm12878_25kb_count[,which(colnames(pcadat_gm12878_25kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_25kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_count_tfbs))

cormat <- cor(pcadat_gm12878_25kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### Percents

```{r}
pcadat_gm12878_25kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_perc.rds")

colnames(pcadat_gm12878_25kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_25kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_25kb_perc_chromstates <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_25kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_chromstates))

cormat <- cor(pcadat_gm12878_25kb_perc_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_25kb_perc_histones <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% histonevars)]

colnames(pcadat_gm12878_25kb_perc_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_histones))

cormat <- cor(pcadat_gm12878_25kb_perc_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_25kb_perc_tfbs <- pcadat_gm12878_25kb_perc[,which(colnames(pcadat_gm12878_25kb_perc) %in% tfbsvars)]

colnames(pcadat_gm12878_25kb_perc_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_perc_tfbs))

cormat <- cor(pcadat_gm12878_25kb_perc_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

####Distances

```{r}
pcadat_gm12878_25kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/Ensemble/PCA/pcadat_gm12878_25kb_dist.rds")

colnames(pcadat_gm12878_25kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_25kb_dist))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_25kb_dist_chromstates <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% chromstatevars)]

colnames(pcadat_gm12878_25kb_dist_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_chromstates))

cormat <- cor(pcadat_gm12878_25kb_dist_chromstates, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_25kb_dist_histones <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% histonevars)]

colnames(pcadat_gm12878_25kb_dist_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_histones))

cormat <- cor(pcadat_gm12878_25kb_dist_histones, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_25kb_dist_tfbs <- pcadat_gm12878_25kb_dist[,which(colnames(pcadat_gm12878_25kb_dist) %in% tfbsvars)]

colnames(pcadat_gm12878_25kb_dist_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_25kb_dist_tfbs))

cormat <- cor(pcadat_gm12878_25kb_dist_tfbs, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### Counts

```{r}
pcadat_gm12878_50kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_count.rds")

colnames(pcadat_gm12878_50kb_count) <- gsub("_count","",colnames(pcadat_gm12878_50kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_50kb_count_chromstates <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_50kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_chromstates))

cormat <- cor(pcadat_gm12878_50kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_50kb_count_histones <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% histonevars)]

colnames(pcadat_gm12878_50kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_histones))

cormat <- cor(pcadat_gm12878_50kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_50kb_count_tfbs <- pcadat_gm12878_50kb_count[,which(colnames(pcadat_gm12878_50kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_50kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_count_tfbs))

cormat <- cor(pcadat_gm12878_50kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### Percents

```{r}
pcadat_gm12878_50kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_perc.rds")

colnames(pcadat_gm12878_50kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_50kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_50kb_perc_chromstates <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_50kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_chromstates))

cormat <- cor(pcadat_gm12878_50kb_perc_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_50kb_perc_histones <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% histonevars)]

colnames(pcadat_gm12878_50kb_perc_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_histones))

cormat <- cor(pcadat_gm12878_50kb_perc_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_50kb_perc_tfbs <- pcadat_gm12878_50kb_perc[,which(colnames(pcadat_gm12878_50kb_perc) %in% tfbsvars)]

colnames(pcadat_gm12878_50kb_perc_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_perc_tfbs))

cormat <- cor(pcadat_gm12878_50kb_perc_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

####Distances

```{r}
pcadat_gm12878_50kb_dist <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/Ensemble/PCA/pcadat_gm12878_50kb_dist.rds")

colnames(pcadat_gm12878_50kb_dist) <- gsub("_dist","",colnames(pcadat_gm12878_50kb_dist))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_50kb_dist_chromstates <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% chromstatevars)]

colnames(pcadat_gm12878_50kb_dist_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_chromstates))

cormat <- cor(pcadat_gm12878_50kb_dist_chromstates, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_50kb_dist_histones <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% histonevars)]

colnames(pcadat_gm12878_50kb_dist_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_histones))

cormat <- cor(pcadat_gm12878_50kb_dist_histones, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_50kb_dist_tfbs <- pcadat_gm12878_50kb_dist[,which(colnames(pcadat_gm12878_50kb_dist) %in% tfbsvars)]

colnames(pcadat_gm12878_50kb_dist_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_50kb_dist_tfbs))

cormat <- cor(pcadat_gm12878_50kb_dist_tfbs, method = "pearson")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### Counts

```{r}
pcadat_gm12878_100kb_count <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_count.rds")

colnames(pcadat_gm12878_100kb_count) <- gsub("_count","",colnames(pcadat_gm12878_100kb_count))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_100kb_count_chromstates <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% chromstatevars)]

colnames(pcadat_gm12878_100kb_count_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_chromstates))

cormat <- cor(pcadat_gm12878_100kb_count_chromstates, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

######Histones

```{r}
histonevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/HistoneModifications"))

pcadat_gm12878_100kb_count_histones <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% histonevars)]

colnames(pcadat_gm12878_100kb_count_histones) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_histones))

cormat <- cor(pcadat_gm12878_100kb_count_histones, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         #tl.cex = .4,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### TFBS

```{r}
tfbsvars <-  gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/tfbs/cell_type_specific/gm12878"))

pcadat_gm12878_100kb_count_tfbs <- pcadat_gm12878_100kb_count[,which(colnames(pcadat_gm12878_100kb_count) %in% tfbsvars)]

colnames(pcadat_gm12878_100kb_count_tfbs) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_count_tfbs))

cormat <- cor(pcadat_gm12878_100kb_count_tfbs, method = "spearman")

corrplot(cormat, 
         type="upper", 
         order="hclust", 
         tl.col="black", 
         tl.srt=90,
         tl.cex = .5,
         col=colorRampPalette(c("blue", "white", "red"))(20),
         cl.pos="n",
         mar = c(0, 0, 0, 0))

##### Percents

```{r}
pcadat_gm12878_100kb_perc <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/Ensemble/PCA/pcadat_gm12878_100kb_perc.rds")

colnames(pcadat_gm12878_100kb_perc) <- gsub("_perc","",colnames(pcadat_gm12878_100kb_perc))
```

######Chromstates

```{r}
chromstatevars <- gsub(".bed","",list.files("Z:/TAD_data_analysis/annotations/BroadHMM"))

pcadat_gm12878_100kb_perc_chromstates <- pcadat_gm12878_100kb_perc[,which(colnames(pcadat_gm12878_100kb_perc) %in% chromstatevars)]

colnames(pcadat_gm12878_100kb_perc_chromstates) <- gsub(paste(c("Gm12878",
                          "-",
                          "_",
                          "count",
                          "Haib",
                          "Sydh",
                          "Uta",
                          "Uw",
                          "Broad",
                          "Uchicago"), collapse = "|"),"", colnames(pcadat_gm12878_100kb_perc_chromstates))

cormat <- cor(pcadat_gm12878_100kb_perc_chromstates, method = "spearman")
